---
title: "Lab 03 - Nobel laureates"
author: "Anahatt Virk"
date: "06/21/2025"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1
```{r nobel-info}
nobel <- read_csv("data/nobel.csv")
```

The dataset contains `r nrow(nobel)` observations and `r ncol(nobel)` variables. Each row contains the information for a Nobel Prize awarded to one laureate. Details such as the recipient's name, gender, and year recieved are present in each row. 

### Exercise 2

```{r nobel-living}
nobel_living <- nobel %>%
  filter(is.na(died_date), !is.na(country), gender !="org")
```

This data frame contains `r nrow(nobel_living)` observations.

### Exercise 3

```{r USA-laureates}
nobel_living <- nobel_living %>%
  mutate(country_us = if_else(country == "USA", "USA", "Other"))

nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))

ggplot(nobel_living_science, aes(y = country_us)) +
  geom_bar() + 
  facet_wrap(~category) + 
  labs(title = "Nobel Prize Laureates by Category and Country", x = "Laureate Count", y ="Country")
```

From the graphs above, it can be seen that Buzzfeed's headline is supported by the data as the US has the most amount of laureates for each scientific category. 

### Exercise 4

```{r birth-country}
nobel_living_science <- nobel_living_science %>%
  mutate(born_country_us = if_else(born_country == "USA", "USA", "Other"))
```

There are `r sum(nobel_living_science$born_country_us == "USA")` Nobel laureates born in the US.

### Exercise 5

```{r US-born}
ggplot(nobel_living_science, aes(y = country_us, fill = born_country_us)) +
  geom_bar(position = "stack") + 
  facet_wrap(~category) + 
  labs(title = "Nobel Prize Laureates by Category and Country", x = "Laureate Count", y ="Country", fill = "Birth Country")
```

Based on these graphs, the data supports Buzzfeed's claim that many US laureates were born in other countries.

### Exercise 6

...
