---
title: "Lab 03 - Nobel laureates"
author: "Anahatt Virk"
date: "06/21/2025"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1
```{r nobel-info}
nobel <- read_csv("data/nobel.csv")
```

The dataset contains `r nrow(nobel)` observations and `r ncol(nobel)` variables. Each row contains the information for a Nobel Prize awarded to one laureate. Details such as the recipient's name, gender, and year recieved are present in each row. 

### Exercise 2

```{r nobel-living}
nobel_living <- nobel %>%
  filter(is.na(died_date), !is.na(country), gender !="org")
```

This data frame contains `r nrow(nobel_living)` observations.

### Exercise 3

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
